On Secure Delegation of SampBQP with a Classical Client

### 2020-01-22 privacy.tex
Add proof sketch of QFHE correctness

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}. We use this particular QFHE because it allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item $\mathsf{QHE.Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
\end{itemize}

@@

\begin{thm}
	\autoref{ProtoPrivateDelegation} is a $\QPIP$ scheme for... (TODO) \Ethan{Just copy from earlier and hope I don't need to rewrite too much}
\end{thm}
\begin{proof}
	TODO
\end{proof}

>>>>

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}. We use this particular QFHE because it allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item $\mathsf{QHE.Dec}$ ``commutes" with measurements. \Ethan{Need to elaborate just a bit more here; i.e. need to mention X/Z only} If the ciphertext is a measurement result, it can also be done classically.
\end{itemize}

@@

\begin{thm}
    \label{QPIP1thm}
	\protoref{ProtoPrivateDelegation} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
\end{thm}
\begin{proof}
	The client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$. \Ethan{Errors terms?}

	Which by the properties of homomoprhic encryption should decode to $\rho$ that is $\varepsilon$-indistinguishable to $C(x)$ \Ethan{Fill in error terms}

	As decoding commutes with measurements, the verifier requests its desired measurements of $\rho$ and decode it.
\end{proof}
